---
title: "Excercise1"
author: "Krishna Bandhakavi"
date: "January 4, 2017"
output: html_document
---

## Excercise 1

1. Given a function, like "mean", match.fun() lets you find a function. Given a function, can you find its name? Why doesn't that make sense in R?

> reverse isnt possible or makes sense as functions can be anonymous or differently named functions can do the same function 

2. Use lapply() and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset.

```{r echo=TRUE}
lapply(mtcars, function(x){sd(x)/mean(x)})
```

3. Use integrate() and an anonymous function to find the area under the curve for the following functions. Use Wolfram Alpha to check your answers.

y = x ^ 2 - x, x in [0, 10]

```{r echo=TRUE}
integrate(function(x){x ^ 2 - x},0,10)
```
y = sin(x) + cos(x), x in [-??, ??]

```{r echo=TRUE}
integrate(function(x){sin(x) + cos(x)},-pi,pi)
```

> this varies from wolphram alpha's answer due to the negative area - add abs to fix that

```{r echo=TRUE}
integrate(function(x){abs(sin(x) + cos(x))},-pi,pi)
```

y = exp(x) / x, x in [10, 20]

```{r echo=TRUE}
integrate(function(x){exp(x)/x},10,20)
```

4. A good rule of thumb is that an anonymous function should fit on one line and shouldn't need to use {}. Review your code. Where could you have used an anonymous function instead of a named function? Where should you have used a named function instead of an anonymous function?
